---
title: "Keep track of full provenance of a package"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/eunjungpark/Documents/dataone/DataONE_2018_Summer_Intern_Project1/fullProv/bobPkg")
```

### Original package using to generate new package
```{r}
library(dataone)
library(datapack)

d1c <- D1Client("STAGING", "urn:node:mnTestARCTIC")
origPkg <- getDataPackage(d1c, identifier = "urn:uuid:5cfda337-4d6b-49a1-ac64-c6bc62d8d439", lazyLoad=TRUE, limit="0MB", quiet=FALSE)
```


### Bundling new package
##### Create metadata in eml
```{r}
source("../createEml.R")
```


##### Create a package
```{r}
dp <- new("DataPackage")
```


##### Add members
```{r}
devtools::install_github("nceas/arcticdatautils")
library(arcticdatautils)

metadataObj <- new("DataObject", format="eml://ecoinformatics.org/eml-2.1.1", filename="./meta.xml")
dp <- addMember(dp, metadataObj)

# Collect lists of files except metadata file
flists <- grep(list.files("."), pattern="\\.xml$", inv=T, value=T)
flists <- grep(flists, pattern="\\.zip$", inv=T, value=T)

# Filter out directory names
flists <- setdiff(flists, list.dirs(recursive = FALSE, full.names = FALSE))

for(o in flists) { 
  obj <- new("DataObject", format=guess_format_id(o), filename=paste("./",o,sep=""))
  dp <- addMember(dp, obj, metadataObj)
}

print(dp)


# add otherEntity
pids <- NULL
for(i in 1:length(flists)) {
  pid <- selectMember(dp, name="sysmeta@fileName", value=flists[i])
  pids <- c(pids, pid)
  flists[i] <- paste("./", flists[i], sep="")
}
entity_df <- data.frame(type="otherEntity", path=flists, pid=pids, format_id=guess_format_id(flists), stringsAsFactors=FALSE)
eml <- eml_add_entities(eml, entity_df)
write_eml(eml, "./meta.xml")
eml_validate("./meta.xml")
print(eml)


# replace metadata file in the package
dp <- replaceMember(dp, metadataObj, replacement="./meta.xml", formatId="eml://ecoinformatics.org/eml-2.1.1")
print(dp)
```


##### Capture provenance
+ Add information of which object is used for new analysis (e.g., (new_analysis.R, "prov:used", Alice's resource map id))
+ Add information of what is the package that the object used belongs to (e.g., (new_analysis.R, "prov:used", "mtcars.csv"))
```{r}
devtools::install_github("nceas/recordr")
library(recordr)
rc <- new("Recordr")

progFiles <- list.files(".", pattern="\\.R$")

if(length(progFiles) > 0) {
  for(i in progFiles) {
    record(rc, paste("./",i,sep=""), tag=i)
  }
  
  # Add provenance into the package
  for(i in 1:length(progFiles)) {
    # capture file names and access types
    vr <- viewRuns(rc, seq=i)
    vrdf <- setNames(data.frame(basename(vr$files$filePath), vr$files$access), c("names","access"))
    vrUsed <- setNames(subset(vrdf, vrdf$access == "read"), c("names","acess"))
    vrDerived <- setNames(subset(vrdf, vrdf$access == "write"), c("names","acess"))
    
    # capture ids for sources (those files used and read)
    sids <- NULL
    for(n in 1:length(vrUsed$names)) {
      sid <- selectMember(dp, name="sysmeta@fileName", value=as.character(vrUsed$names[n]))
      sids <- c(sids, sid)
      
      # add a connection to Alice's package as a relationship into Bob's package
      # information of the original package that the source data belongs to
      if(!is.element(origPkg@resmapId, sids)) {
        sids <- c(sids, origPkg@resmapId) 
      }
      
      # information of the object in the original package that the Bob's analysis used
      sid <- selectMember(origPkg, name="sysmeta@fileName", value=as.character(vrUsed$names[n]))
      sids <- c(sids, sid)
      #sids <- c(sids, as.character(vrUsed$names[n]))
    }
    
    # capture ids for outputs (those files derived)
    oids <- NULL
    for(o in 1:length(vrDerived$names)) {
      oid <- selectMember(dp, name="sysmeta@fileName", value=as.character(vrDerived$names[o]))
      oids <- c(oids, oid)
    }
    
    # capture id for program script
    pid <- selectMember(dp, name="sysmeta@fileName", value=progFiles[i])
    
    # create provenance relationships
    dp <- describeWorkflow(dp, sources=sids, program=pid, derivations=oids)
  }
  
  print(dp)  
}
```

### Publish package to DataONE Test node
```{r}
#d1c <- D1Client("STAGING", "urn:node:mnTestARCTIC")
#pkgId <- uploadDataPackage(d1c, dp, public=TRUE, quiet=FALSE)
```


### Retrieve during transparancy 
##### Download package from DataONE
```{r}
fullProvPkg <- getDataPackage(d1c, identifier = "urn:uuid:7255080f-86e5-422a-8360-117cf80b6f0b", lazyLoad=TRUE, limit="0MB", quiet=FALSE)
```

##### Get provenance relationships
```{r}
saveWidth <- getOption("width")
options(width=120)
relFullProv <- getRelationships(fullProvPkg, condense=T)
prov <- subset(relFullProv, predicate=="prov:used" | predicate =="prov:wasDerivedFrom" | predicate=="prov:wasGeneratedBy")
```

##### Replace ids with names
```{r}
provPlan <- subset(relFullProv,predicate == "prov:hadPlan")
provAsso <- subset(relFullProv,predicate == "prov:qualifiedAssociation")
provAsso$object <- provPlan$object[match(provAsso$object, provPlan$subject)]
indx <- match(prov$subject, provAsso$subject, nomatch = 0)
prov$subject[indx != 0] <- provAsso$object[indx]
indx <- match(prov$object, provAsso$subject, nomatch = 0)
prov$object[indx != 0] <- provAsso$object[indx]
prov <- data.frame(lapply(prov, as.character), stringsAsFactors=FALSE)
prov
```

<!--
##### Filter out unnecessary relationships
```{r}
provSimp <- subset(prov, predicate=="prov:used" | predicate=="prov:wasGeneratedBy")
provSimp
```
-->