---
title: "Bundling captured provenance into the package and publishing to DataONE"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/eunjungpark/Documents/dataone/DataONE_2018_Summer_Intern_Project1/bundling/new")
```

### Create a new package (assume that new products have created)
##### Create metadata in eml
```{r}
library(EML)

# create metadata information
coverage <- set_coverage(beginDate="2018-07-03", endDate="2018-07-20", 
                         geographicDescription="Chicago", 
                         west=-87.623177, east=-87.623177, 
                         north=41.881832, south=41.881832)
person <- as.person("Seokki Lee <slee195@hawk.iit.edu> [cre]")
slee <- as(person, "creator")
contact <- new("contact", 
               individualName = slee@individualName, 
               electronicMail = slee@electronicMailAddress, 
               organizationName = "IIT", phone="000-000-0000")
pubDate <- "2018-07-03"
title <- "Bundling test for EVOS GoA"
abstract <- "test abs"

dataset <- new("dataset", 
               title=title, 
               creator=slee, 
               pubDate=pubDate, 
               abstract=abstract, 
               coverage=coverage, 
               contact=contact)
eml <- new("eml", system="uuid", dataset=dataset)

# write it into a file
write_eml(eml, "./meta.xml")

# check the written metadata file is valid
eml_validate("./meta.xml")

eml
```


##### Create a package with newly generated objects
+ Create a package
```{r}
library(dataone)
library(datapack)

dp <- new("DataPackage")
```

+ Add metadata into the package
```{r}
metadataObj <- new("DataObject", format="eml://ecoinformatics.org/eml-2.1.1", filename="./meta.xml")
dp <- addMember(dp, metadataObj)
dp
```

+ Add objects into the package (TODO: define file type, e.g., text/csv if file is csv)
```{r}
# collect lists of files except metadata file
flists <- grep(list.files("."), pattern="\\.xml$", inv=T, value=T)
flists <- grep(flists, pattern="\\.zip$", inv=T, value=T)

# filter out directory names
flists <- setdiff(flists, list.dirs(recursive = FALSE, full.names = FALSE))

for(o in flists) { 
  obj <- new("DataObject", filename=paste("./",o,sep=""))
  dp <- addMember(dp, obj, metadataObj)
}

dp
```


<!--
```{r}
# collect lists of files except metadata file
#flists <- grep(list.files("./new/"), pattern="\\.xml$", inv=T, value=T)

# collect the extensions from the list
#for (i in 1:length(flists)) {
#  types <- c(types,sub("([^.?]*)","",flists[i]))
#}

#for (type in unique(types)) {
#  objs = list.files("./new/", pattern=paste("\\",type,"$",sep=""))
  
#  for(o in objs) { 
#    obj <- new("DataObject", format="text/csv", filename=paste("./new",o,sep=""))
#    dp <- addMember(dp, obj, metadataObj)
#  }
#}

#dp
```


+ add scripts into the package
```{r}
#progFiles = list.files("./new/", pattern="\\.R$")

#for(i in progFiles) { 
#  progObj <- new("DataObject", format="application/R", filename=i)
#  dp <- addMember(dp, progObj, metadataObj)
#}

#dp
```

+ add images into the package
```{r}
#outFiles = list.files("./new/", pattern="\\.png$")

#for(i in outFiles) { 
#  outObj <- new("DataObject", format="image/png", filename=i)
#  dp <- addMember(dp, outObj, metadataObj)
#}

#dp
```
-->


### Record provenance for the computational scripts
##### Initialize recordr and collect the list of script files
```{r}
library(recordr)
rc <- new("Recordr")
progFiles <- list.files(".", pattern="\\.R$")
progFiles
```

##### Capture provenance for each script
```{r}
for(i in progFiles) {
  record(rc, paste("./",i,sep=""), tag=i)
}
```

##### List the records
```{r}
listRuns(rc)
```

##### View each record in detail
```{r}
for(i in 1:length(progFiles)) {
  viewRuns(rc, seq=i) 
}
```


### Add the captured provenance into the package
+ Collect the file name and file access type (e.g., read or write)
+ Group the provenance information into two sets (i.e., used and derived)
+ For each file used/derived, collect their ids from the package created above (using "selectMember")
+ Generate and add the provenance relationship into the package (using "describeWorkflow")
```{r}
for(i in 1:length(progFiles)) {
  # capture file names and access types
  vr <- viewRuns(rc, seq=i)
  vrdf <- setNames(data.frame(basename(vr$files$filePath), vr$files$access), c("names","access"))
  vrUsed <- setNames(subset(vrdf, vrdf$access == "read"), c("names","acess"))
  vrDerived <- setNames(subset(vrdf, vrdf$access == "write"), c("names","acess"))
  
  # capture ids for sources (those files used and read)
  sids <- NULL
  for(n in 1:length(vrUsed$names)) {
    sid <- selectMember(dp, name="sysmeta@fileName", value=as.character(vrUsed$names[n]))
    sids <- c(sids, sid)
  }
  
  # capture ids for outputs (those files derived)
  oids <- NULL
  for(o in 1:length(vrDerived$names)) {
    oid <- selectMember(dp, name="sysmeta@fileName", value=as.character(vrDerived$names[o]))
    oids <- c(oids, oid)
  }
  
  # capture id for program script
  pid <- selectMember(dp, name="sysmeta@fileName", value=progFiles[i])
  
  # create provenance relationships
  dp <- describeWorkflow(dp, sources=sids, program=pid, derivations=oids)
}

dp
```

### Publish the package to DataONE
```{r}
#d1c <- D1Client("STAGING", "urn:node:mnTestARCTIC")
#pkgId <- uploadDataPackage(d1c, dp, public=TRUE, quiet=FALSE)
```