---
title: "Transparancy of the provenance information for hydrocarbons use case in DataONE"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/eunjungpark/Documents/dataone/DataONE_2018_Summer_Intern_Project1/transparency")
```

### Retrieve provenance information from the package (Option 1)
#### Get package from production node of Gulf of Alaska Data Portal (GOA)
```{r}
library(dataone)
library(datapack)
d1c <- D1Client("PROD", "urn:node:GOA")
pkg <- getDataPackage(d1c, identifier = "urn:uuid:1d23e155-3ef5-47c6-9612-027c80855e8d", lazyLoad=TRUE, limit="0MB", quiet=FALSE)
saveWidth <- getOption("width")
options(width=120)
```

#### Retrieve information for the package
```{r}
rels <- getRelationships(pkg, condense=T)
rels
```

#### Retrieve provenance information from the package
```{r}
prov <- subset(rels, predicate=="prov:used" | predicate =="prov:wasDerivedFrom" | predicate=="prov:wasGeneratedBy")
prov
```

#### Replace ids with names
+ Create a data frame that contains id->name relationship
```{r}
provPlan <- subset(rels,predicate == "prov:hadPlan")
provAsso <- subset(rels,predicate == "prov:qualifiedAssociation")
provPlan
provAsso
```
```{r}
provAsso$object <- provPlan$object[match(provAsso$object, provPlan$subject)]
provAsso
```

+ Replace ids with names in the provenance relationship
```{r}
indx <- match(prov$subject, provAsso$subject, nomatch = 0)
prov$subject[indx != 0] <- provAsso$object[indx]
indx <- match(prov$object, provAsso$subject, nomatch = 0)
prov$object[indx != 0] <- provAsso$object[indx]
prov
```

#### Convert data fram columns from factors to chars
```{r}
prov <- data.frame(lapply(prov, as.character), stringsAsFactors=FALSE)
```

#### Create RDF and store into a file
```{r}
library(rdflib)
```

<!--
```{r}
rdf <- rdf()
for (i in 1:nrow(prov)) rdf_add(rdf,prov$object[i],prov$predicate[i],prov$subject[i], subjectType="uri", objectType="uri")
options(rdf_print_format = "rdfxml")
rdf_serialize(rdf, "./results/prov.rdfxml")
rdf
```

#### Convert rdf file to dot and then to pdf to visualize
```{r}
system("rapper --output dot /Users/eunjungpark/Documents/dataone/DataONE_2018_Summer_Intern_Project1/transparency/results/prov.rdfxml > /Users/eunjungpark/Documents/dataone/DataONE_2018_Summer_Intern_Project1/transparency/results/prov.dot")
system("dot -Tpdf /Users/eunjungpark/Documents/dataone/DataONE_2018_Summer_Intern_Project1/transparency/results/prov.dot > /Users/eunjungpark/Documents/dataone/DataONE_2018_Summer_Intern_Project1/transparency/results/prov.pdf")
```
```{r, out.width="950px", out.height="600px"}
knitr::include_graphics("./results/prov.pdf")
```


#### Generate Simpler Workflow
-->

```{r}
provSimp <- subset(prov, predicate=="prov:used" | predicate=="prov:wasGeneratedBy")
provSimp
```

```{r}
provSimp <- data.frame(lapply(provSimp, as.character), stringsAsFactors=FALSE)
```

```{r}
rdfSimp <- rdf()
for (i in 1:nrow(provSimp)) rdf_add(rdfSimp, provSimp$object[i], provSimp$predicate[i], provSimp$subject[i], subjectType="uri", objectType="uri")
options(rdf_print_format = "rdfxml")
rdf_serialize(rdfSimp, "./results/provSimp.rdfxml")
rdf
```

```{r}
system("rapper --output dot ./results/provSimp.rdfxml > ./results/provSimp.dot")
system("dot -Tpdf ./results/provSimp.dot > ./results/provSimp.pdf")
```
```{r, out.width="950px", out.height="600px"}
knitr::include_graphics("./results/provSimp.pdf")
```


```{r}
provNoPred <- provSimp
indx <- match(provNoPred$predicate, "prov:wasGeneratedBy", nomatch = 0)
provNoPred$predicate[indx != 0] <- "prov:generated"
indx <- match(provNoPred$predicate, "prov:used", nomatch = 0)
provNoPred$predicate[indx != 0] <- "prov:wasUsedBy"
provNoPred <- data.frame(lapply(provNoPred, as.character), stringsAsFactors=FALSE)
provNoPred
```

```{r}
rdfSimp <- rdf()
for (i in 1:nrow(provNoPred)) rdf_add(rdfSimp, provNoPred$object[i], provNoPred$predicate[i], provNoPred$subject[i], subjectType="uri", objectType="uri")
options(rdf_print_format = "rdfxml")
rdf_serialize(rdfSimp, "./results/provTest.rdfxml")
rdf
```

```{r}
system("rapper --output dot ./results/provTest.rdfxml > ./results/provSimp.dot")
system("dot -Tpdf ./results/provTest.dot > ./results/provTest.pdf")
```
```{r, out.width="950px", out.height="600px"}
knitr::include_graphics("./results/provTest.pdf")
```


<!--
#### Using resource map
+ Collect only provenance information
```{r}
relsNoCondense <- getRelationships(pkg)
provRels <- relsNoCondense[ grep("prov", relsNoCondense$predicate), ]
provRels
```

+ Create a new resource map and save into a file
```{r}
resMapId <- sprintf("%s%s", "resourceMap_", uuid::UUIDgenerate())  
resMap <- new("ResourceMap", id=resMapId)
resMap <- createFromTriples(resMap, provRels, getIdentifiers(pkg))
serializeRDF(resMap, "./data/rdf-prov-uncleaned.xml")
```

+ To get a clean workflow, users have to manually go through the resource map
```{r}
system("rapper --output dot /Users/eunjungpark/Documents/dataone/DataONE_2018_Summer_Intern_Project1/transparency/data/rdf-prov > /Users/eunjungpark/Documents/dataone/DataONE_2018_Summer_Intern_Project1/transparency/results/provFromRM.dot")
system("dot -Tpdf /Users/eunjungpark/Documents/dataone/DataONE_2018_Summer_Intern_Project1/transparency/results/provFromRM.dot > /Users/eunjungpark/Documents/dataone/DataONE_2018_Summer_Intern_Project1/transparency/results/provFromRM.pdf")
```
```{r, out.width="950px", out.height="300px"}
knitr::include_graphics("./results/provFromRM.pdf")
```
-->

#### Visualize provenance in YesWorkflow (YW)
##### Capture provenance needed for generating YW comments
```{r}
provYwDef <- subset(prov, predicate == "prov:wasDerivedFrom")
provYwUsed <- subset(prov, predicate == "prov:used")
provYwDef
provYwUsed
```

##### Create data frame which shows subject=output, predicate=program, and object=input
```{r}
provYwDef$predicate <- provYwUsed$subject[match(provYwDef$object, provYwUsed$object, nomatch=0)]
provYwDef
```

##### Split data frame by the program
```{r}
ins <- split(provYwDef$object, provYwDef$predicate)
outs <- split(provYwDef$subject, provYwDef$predicate)
ins
outs
```

##### Generate YW comments for inputs and outputs for each group
```{r}
ins <- data.frame(lapply(as.data.frame(ins), as.character), stringsAsFactors = FALSE)
for(i in names(ins)) ins[[i]] <- paste("#@in ", sub("\\..*","",ins[[i]]), " @URI file:", ins[[i]],sep="")
ins
outs <- data.frame(lapply(as.data.frame(outs), as.character), stringsAsFactors = FALSE)
for(i in names(outs)) outs[[i]] <- paste("#@out ", sub("\\..*","",outs[[i]]), " @URI file:", outs[[i]],sep="")
outs
```

##### Combine YW comments in each group
```{r}
inouts <- rbind(ins,outs)
inouts
```

##### Create file, write comments into the corresponding file, and generate YW
```{r}
for(i in names(inouts)) {
  filename <- paste("YW",i,sep="")
  name <- paste("test/",filename,sep="")
  file.create(name)
  write(paste("#@begin",sub("\\..*","",i)),file=name,append = TRUE)
  write(unique(ins[[i]]),file=name,append=TRUE)
  write(paste("#@begin",sub("\\..*","",i), "@desc", i),file=name,append = TRUE)
  write(unique(inouts[[i]]),file=name,append=TRUE)
  write(paste("#@end",sub("\\..*","",i)),file=name,append = TRUE)
  write(unique(outs[[i]]),file=name,append=TRUE)
  write(paste("#@end",sub("\\..*","",i)),file=name,append = TRUE)
  system(paste("java -jar /Users/eunjungpark/Documents/dataone/DataONE_2018_Summer_Intern_Project1/transparency/yw_jar/yesworkflow-0.2.1-SNAPSHOT-jar-with-dependencies.jar graph ",name," -c graph.view=combined -c graph.layout=tb > ",sub("\\..*","",name),".gv",sep=""))
  system(paste("dot -Tpdf ",sub("\\..*","",name),".gv > ",sub("\\..*","",name),".pdf", sep=""))
  #system(paste("cat /Users/eunjungpark/Documents/dataone/DataONE_2018_Summer_Intern_Project1/transparency/",sub("\\..*","",name),sep = ""),intern = TRUE)
}
```


```{r}
system("cat /Users/eunjungpark/Documents/dataone/DataONE_2018_Summer_Intern_Project1/transparency/test/YWTotal_PAH_and_Al.R",intern = TRUE)
system("cat /Users/eunjungpark/Documents/dataone/DataONE_2018_Summer_Intern_Project1/transparency/test/YWhcdbSites.R",intern = TRUE)
```

<!--
```{r, out.width="950px", out.height="600px"}
knitr::include_graphics("./test/YWTotalPAH.pdf")
knitr::include_graphics("./test/YWhcdbSites.pdf")
```
-->

##### Run, e.g, make.sh (below script block can be stored in a single executable file)
```{r, engine = 'bash', eval = FALSE}
# define base directories
export EXAMPLE_DIR=.
export PROJECT_ROOT=.

# define lcoation of YesWorkflow jar file
export YW_JAR="${PROJECT_ROOT}/yw_jar/yesworkflow-0.2.1-SNAPSHOT-jar-with-dependencies.jar"

# define command for running YesWorkflow
export YW_CMD="java -jar $YW_JAR"

# destination of facts, views and query results
export SCRIPT_DIR=${EXAMPLE_DIR}/scripts
export RESULTS_DIR=${EXAMPLE_DIR}/results

mkdir -p $RESULTS_DIR

# generate workflow using commented script
graph_name="aoos_retro_wf_graph"
$YW_CMD graph "./scripts/aoos.R" \
    -c graph.view=combined \
    -c graph.layout=tb \
      > $RESULTS_DIR/$graph_name.gv
dot -Tpdf $RESULTS_DIR/$graph_name.gv > $RESULTS_DIR/$graph_name.pdf
dot -Tsvg $RESULTS_DIR/$graph_name.gv > $RESULTS_DIR/$graph_name.svg
```

```{r, out.width="950px", out.height="600px"}
#system("source ./make.sh")
knitr::include_graphics("./results/aoos_retro_wf_graph.pdf")
```


### Record provenance using recordr (Option2)
```{r}
source("./setup.R")
library(recordr)
rc <- new("Recordr")
```

#### Record provenance for the first script
```{r}
record(rc, "./scripts/Total_PAH_and_Alkanes_GoA_Hydrocarbons_Clean.R", tag="total_pah_and_alkanes_goa_hydrocarbons_clean script1")
```

#### Record provenance for the second script
```{r}
record(rc, "./scripts/hcdbSites.R", tag="hcdbsites script2")
```

#### List the records
```{r}
listRuns(rc)
```

#### View each record in detail
```{r}
viewRuns(rc, tag="script1")
viewRuns(rc, tag="script2")
```

