---
title: "R script that automatically generate and publish a package"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

* A script for creating a package (including all the necessary intermediate steps) inside a tale. By running this script, the package created will be published to DataONE repository.
```{r}
library("dataone")
library("datapack")
library("EML")
```
### Create a new package
```{r}
dp <- new("DataPackage")
```

### Add objects into the package
##### Metadata
```{r}
metadataObj <- new("DataObject", format="eml://ecoinformatics.org/eml-2.1.1", 
                   filename="/Users/eunjungpark/Documents/dataone/AOOS/urn_uuid_1d23e155_3ef5_47c6_9612_027c80855e8d/data/metadata.xml")
dp <- addMember(dp, metadataObj)
dp
```

##### Add sources
+ add PAH.csv, Alkane.csv, Sample.csv, Non-EVOS_SINs.csv
```{r}
sourceObj1 <- new("DataObject", 
                 format="text/csv",
                 filename="/Users/eunjungpark/Documents/dataone/AOOS/urn_uuid_1d23e155_3ef5_47c6_9612_027c80855e8d/data/PAH.csv")
dp <- addMember(dp, sourceObj1, metadataObj)

sourceObj2 <- new("DataObject", 
                 format="text/csv",
                 filename="/Users/eunjungpark/Documents/dataone/AOOS/urn_uuid_1d23e155_3ef5_47c6_9612_027c80855e8d/data/Alkane.csv")
dp <- addMember(dp, sourceObj2, metadataObj)

sourceObj3 <- new("DataObject", 
                 format="text/csv",
                 filename="/Users/eunjungpark/Documents/dataone/AOOS/urn_uuid_1d23e155_3ef5_47c6_9612_027c80855e8d/data/Sample.csv")
dp <- addMember(dp, sourceObj3, metadataObj)

sourceObj4 <- new("DataObject", 
                 format="text/csv",
                 filename="/Users/eunjungpark/Documents/dataone/AOOS/urn_uuid_1d23e155_3ef5_47c6_9612_027c80855e8d/data/Non-EVOS_SINs.csv")
dp <- addMember(dp, sourceObj4, metadataObj)
dp
```

##### Add program scripts
```{r}
mergeObj <- new("DataObject", 
               format="application/R",
               filename="/Users/eunjungpark/Documents/dataone/AOOS/urn_uuid_1d23e155_3ef5_47c6_9612_027c80855e8d/data/Total_PAH_and_Alkanes_GoA_Hydrocarbons_Clean.R")
dp <- addMember(dp, mergeObj, metadataObj)

genObj <- new("DataObject",
              format="application/R",
              filename="/Users/eunjungpark/Documents/dataone/AOOS/urn_uuid_1d23e155_3ef5_47c6_9612_027c80855e8d/data/hcdbSites.R")
dp <- addMember(dp, genObj, metadataObj)
dp
```

##### Add output artifacts
```{r}
outputObj1 <- new("DataObject",
                  format="text/csv",
                  filename="/Users/eunjungpark/Documents/dataone/AOOS/urn_uuid_1d23e155_3ef5_47c6_9612_027c80855e8d/data/Total_Aromatic_Alkanes_PWS.csv")
dp <- addMember(dp, outputObj1, metadataObj)

outputObj2 <- new("DataObject",
                  format="image/png",
                  filename="/Users/eunjungpark/Documents/dataone/AOOS/urn_uuid_1d23e155_3ef5_47c6_9612_027c80855e8d/data/hcdbSamplesGOA.png")
dp <- addMember(dp, outputObj2, metadataObj)

outputObj3 <- new("DataObject",
                  format="image/png",
                  filename="/Users/eunjungpark/Documents/dataone/AOOS/urn_uuid_1d23e155_3ef5_47c6_9612_027c80855e8d/data/hcdbSampleLocs.png")
dp <- addMember(dp, outputObj3, metadataObj)
dp
```

##### additional objs if exists
```{r}
provObj <- new("DataObject",
               format="image/png",
               filename="/Users/eunjungpark/Documents/dataone/AOOS/urn_uuid_1d23e155_3ef5_47c6_9612_027c80855e8d/data/pros_prov_YW_AOOS.png")
dp <- addMember(dp, provObj, metadataObj)
dp
```



```{r}
#3 add provenance information to the package
dp <- describeWorkflow(dp, sources=sourceObj1, program=mergeObj, derivations=outputObj1)
dp <- describeWorkflow(dp, sources=sourceObj2, program=mergeObj, derivations=outputObj1)
dp <- describeWorkflow(dp, sources=sourceObj3, program=mergeObj, derivations=outputObj1)
dp <- describeWorkflow(dp, sources=sourceObj4, program=mergeObj, derivations=outputObj1)
dp <- describeWorkflow(dp, sources=outputObj1, program=genObj, derivations=outputObj2)
dp <- describeWorkflow(dp, sources=outputObj1, program=genObj, derivations=outputObj3)

dp
```

```{r}
#4 publish the package to DataONE
#d1c <- D1Client("STAGING", "urn:node:mnTestARCTIC")
#pkgId <- uploadDataPackage(d1c, dp, public=TRUE, quiet=FALSE)
```

